\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-26 paper/subdocuments/results.Rnw
added the famous ben-plot

>>>>

<<benplot>>=
### libs
library(reshape, quietly=TRUE, warn.conflicts = FALSE)
library(foreign)
library(dplyr)
library(reldist)
library(ggplot2)

### Fetch Ginis from different survey data
number_ticks <- function(n) {function(limits) pretty(limits, n)}
swissGini<-read.csv("../../data/swissGini.csv",header=TRUE,sep=";")

### Ginis from Bens File (for imputed gap)
ben <- filter(read.dta("../../data/estv-gini-kt.dta"),kanton=="CH2")

### and for the rest of Ginis:
estv <- read.dta("../../data/steuerdaten20140522_stata12.dta")

estv_gini <- estv %.% 
  filter(kanton=="CH",eink_art=="Nach steuerbarem Einkommen",fall=="Normalfälle",anz_pflichtige>0,steuerperiode!=1945.5) %.% 
  select(steuerperiode, steink, kanton, eink_ll, eink_ul,anz_pflichtige) %.%
  group_by(factor(steuerperiode)) %.%
  mutate(mean_steink=steink/anz_pflichtige) %.%
  summarise(gini(mean_steink,weights=anz_pflichtige))

names(estv_gini) <- c("Year","FTA")
estv_gini$Year<-as.numeric(as.character(estv_gini$Year))
estv_gini$Year[estv_gini$Year<2003] <- estv_gini$Year[estv_gini$Year<2003]-2

all_gini <- data.frame("Year"=seq(1916,2012,by=0.5))
all_gini$FTA <- estv_gini$FTA[match(all_gini$Year,estv_gini$Year)]
all_gini$HBS <- swissGini$HABE[match(all_gini$Year,swissGini$Year)]
all_gini$EU.SILC <- swissGini$EU.SILC[match(all_gini$Year,swissGini$Year)]
all_gini$LIS <- swissGini$LIS[match(all_gini$Year,swissGini$Year)]
all_gini$FTA_imp <- ben$gini[match(all_gini$Year,ben$jahr)]

all_gini_long<-melt(all_gini,id="Year")

names(all_gini_long) <- c("Year","Data","Gini")
ggplot(data=na.omit(all_gini_long),
  aes(y=Gini,x=Year,shape=Data,linetype=Data))+
  ylab("Gini from different sources") +
  scale_y_continuous(limits=c(0.18,0.4)) +
  scale_x_continuous(limits=c(1915,2012),breaks=number_ticks(10)) +
  geom_point(size=3)+
  geom_line()+
  theme_bw()+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))
